The Next Economic Era

### 2014-02-13 draft1.tex
bibliography + 2 pages

\usepackage{cite}

@@

			The first point is that capitalism is a system. But who decided upon this system in the first place? Who is enforcing it now? If I'd like to live as a communist or something 
			else from today, could I?

@@

>>>>

%\usepackage{cite}
\bibliographystyle{plain}

@@

			The first point is that capitalism is a system. But who decided upon this system in the first place? Who is enforcing it now? If I'd like to live as a communist or something 
			else from today, could I? There are many different aspects to capitalism. Some of these were developed later than others, and are adopted differently around 
			the world. Regardless, I would argue that the very core of capitalism has always been twofold, and evolved rather naturally: the use of a single currency to trade, and Adam Smith's famous 
			"invisible hand of the market" \cite{Smith1776}.\

			I used the term "naturally" to describe the evolution of capitalism, and it's worth noting what I mean by this as it will be a recurring way of looking at things throughout the book. What I mean is 
			there exists a tendency towards it by virtue of its inherent simplicity, or because of some aspect of generally universal human nature. Let's look at the idea of currency to make this a bit more 
			concrete. It will also give some sense to our subsequent discussion of the so called invisible hand. Currency doesn't really have much purpose in a world where each individual is completely 
			self-sufficient. If I were to produce my own clothes, food, and so on, I wouldn't really need to trade things with others. In fact, assuming people general need and want the same things, this even takes 
			into account altruistic tendencies: if I wanted to give you something as a present, I could give you something I produced. Let's take this altruism into account in our definition of "self-sufficient", just to be 
			very careful in our generalizations right from the start. There may be a world out there with completely self-sufficient intelligent creatures, each living out their monumentally independent lives, but it 
			would be very different from ours. People do in fact often want to trade. One way of doing so, and as was done for quite a while before the advent of currency, would be to barter. However as the 
			number of different items grows, the number of possible two-way trades grows combinatorially. For example a cow might be worth one hundred pens, or twenty shirts, or perhaps a couple cell phones. It 
			gets harder and harder to keep track of all these "value conversions". In addition, trades become much less liquid. If you gave me a cow, but the milkman doesn't need one, I'll have a hard time getting milk. 
			And thus, currency comes to the rescue, offering infinitely more simplicity in trade, storage of value and as a unit of account. Any one good or service could be used as currency, but with different 
			practical advantages. We just so happened to begin with rocks, seashells and precious metals, and move on to completely subject fiat currency from there. And so we see that there is a very "natural" aspect 
			to the adoption of currency throughout the world.

@@

	% BIBLIOGRAPHY USING BIBTEX
	\bibliography{bibliography}
